Data Analysis Expanded

### 2019-08-20 data_analysis/data_analysis_expanded.Rmd
another data analysis update

```{r s1_m3_d}
#s1_m3_d <- rre::gof_criterion(list_of_samples[[1]], 
#                              lambda_vec = seq(450,550,by=10),
#                              multiplier = 200,
#                              c_seq_len = 200,
#                              starts = data.frame(alpha = 0.001738,
#                                                  delta = 0.001744))
```
```{r s1_m3_d_print, results = 'asis'}
#s1_m3_d %>% report_results_2(., list_of_samples[[1]], report_eta = T)
```
<br><br>
<br><br>

@@

```{r s2_m3_e}
# Selected lambda was on the edge of previous grid, lets try again:
#s2_m3_e <- rre::gof_criterion(list_of_samples[[2]], 
#                              lambda_vec = seq(150,300,by=5),
#                              multiplier = 100,
#                              c_seq_len = 499,
#                              starts = data.frame(alpha = 0.004656,
#                                                  delta = 0.0025668))
```
```{r s2_m3_e_print, results = 'asis'}
#s2_m3_e %>% report_results_2(., list_of_samples[[2]], report_eta =T)
```
<br><br>
<br><br>

@@

```{r s3_m3_e}
# Selected lambda was on the edge of previous grid, lets try again:
#s3_m3_e <- rre::gof_criterion(list_of_samples[[3]], 
#                              lambda_vec = seq(150, 250, by=5),
#                              multiplier = 100,
#                              c_seq_len = 499,
#                              starts = data.frame(alpha = 0.0014137,
 #                                                 delta = 0.001367))
```
```{r s3_m3_e_print, results = 'asis'}
#s3_m3_e %>% report_results_2(., list_of_samples[[3]], report_eta = T)
```
<br><br><br><br>

>>>>

```{r s1_m3_d}
s1_m3_d <- rre::gof_criterion(list_of_samples[[1]],
                             lambda_vec = seq(500,650,by=10),
                             multiplier = 200,
                             c_seq_len = 200,
                             starts = data.frame(alpha = 0.001738,
                                                 delta = 0.001744))
```
```{r s1_m3_d_print, results = 'asis'}
s1_m3_d %>% report_results_2(., list_of_samples[[1]], report_eta = T)
```
<br><br>
<br><br>

@@

```{r s2_m3_e}
# Selected lambda was on the edge of previous grid, lets try again:
s2_m3_e <- rre::gof_criterion(list_of_samples[[2]],
                             lambda_vec = seq(150,300,by=10),
                             multiplier = 100,
                             c_seq_len = 100,
                             starts = data.frame(alpha = 0.004656,
                                                 delta = 0.0025668))
```
```{r s2_m3_e_print, results = 'asis'}
s2_m3_e %>% report_results_2(., list_of_samples[[2]], report_eta =T)
```
<br><br>
<br><br>

@@

```{r s3_m3_e}
# Selected lambda was on the edge of previous grid, lets try again:
s3_m3_e <- rre::gof_criterion(list_of_samples[[3]],
                             lambda_vec = seq(150, 250, by=10),
                             multiplier = 100,
                             c_seq_len = 100,
                             starts = data.frame(alpha = 0.0014137,
                                                delta = 0.001367))
```
```{r s3_m3_e_print, results = 'asis'}
s3_m3_e %>% report_results_2(., list_of_samples[[3]], report_eta = T)
```
<br><br><br><br>
